Synthesizing Quotient Lenses

### 2018-03-11 papers/QuotientLenses/main.tex
add additional question

\item The remaining eight benchmarks were derived from datasets found at 
  data.gov. These datasets include census
  population data, wage comparison data, demographics statistics data and
  crime index data. We chose these datasets since they were stored in XML, CSV
  and RDF formats which are more easily specified using regular expressions than
  plain text or PDF documents.  \BCP{Besides differing formats, why did we
    include these eight new 
    ones?  Are they significantly different (more complex, exercising
    different features of the synthesis algorithm or QRE syntax,
    ...)?}\afm{Solomon, could you fill this out?}
    \sam{Well these data formats were the ones I was playing with before we got
    the Augeus and flashfill examples. I chose them simply because they had
    formats which could be expressed using regular expressions. They basically
    use the same QREs as the flashfill and augeus examples, mostly the project
    QRE. The fields in these files are occur in the same order in each record;
    we tried using the perm combinator anyways but the synthesis algorithm took
    too long. I do not think that they are significantly different from the
    flashfill and augues examples.}
\end{enumerate}

>>>>

\item The remaining eight benchmarks were derived from datasets found at 
  data.gov. These datasets include census
  population data, wage comparison data, demographics statistics data and
  crime index data. We chose these datasets since they were stored in XML, CSV
  and RDF formats which are more easily specified using regular expressions than
  plain text or PDF documents.  \BCP{Besides differing formats, why did we
    include these eight new 
    ones?  Are they significantly different (more complex, exercising
    different features of the synthesis algorithm or QRE syntax,
    ...)?}\afm{Solomon, could you fill this out?}
    \sam{Well these data formats were the ones I was playing with before we got
    the Augeus and flashfill examples. I chose them simply because they had
    formats which could be expressed using regular expressions. They basically
    use the same QREs as the flashfill and augeus examples, mostly the project
    QRE. The fields in these files are occur in the same order in each record;
    we tried using the perm combinator anyways but the synthesis algorithm took
    too long. I do not think that they are significantly different from the
    flashfill and augues examples.}\afm{So would it be appropriate to say it was
    these were merely the first examples in the data.gov website whose languages
    are regular?}
\end{enumerate}
